---
title: "Linear Model with Prediction"
author: "Ezra Licciardi"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
---


```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
```

```{r, eval=TRUE, warning=FALSE}
url <- "https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt"
mydata <- read.csv(file=url,sep="",header=TRUE)  
```

# Introduction

We are looking at data procured from RVLS regarding "Physical Strength and Job Performance". We are exploring this data to see if any statistically significant correlations exist in the data or if the data is meaningfully related.

$H_0$ There are no statistically meaningful relation in the data.

$H_A$ There are statistically meaningful relation in the data.


# Methods

```{r}
glimpse(mydata)
model1 <- lm(SIMS~ARM,data=mydata)
model2 <- lm(SIMS~GRIP,data=mydata)
model3 <- lm(SIMS~ARM+GRIP,data=mydata)

sims <- mean(mydata$SIMS)
target1 <- data.frame(ARM=88,GRIP=94)


```

Looking at the data provided they are all of data type: double meaning that they are continuous numerical data. This means that all problems in this write up will be of the numerical~numerical type.

With the CandP helper file we will use scatter plots, correlation coefficients, and linear regression to explore the data.

# Results

## Graphical Results

``` {r include = TRUE, echo = FALSE}
ggplot(mydata, aes(x = ARM, y = SIMS)) +
  geom_point() +
  labs(title = "SIMS ~ ARM",x = "ARM",y = "SIMS") + 
  theme(plot.title = element_text(hjust = 0.5, size = 20)) +
  geom_smooth(method=lm) 

ggplot(mydata, aes(x = GRIP, y = SIMS)) +
  geom_point() +
  labs(title = "SIMS ~ GRIP",x = "GRIP",y = "SIMS") + 
  theme(plot.title = element_text(hjust = 0.5, size = 20)) +
  geom_smooth(method=lm)

ggplot(mydata, aes(x = ARM+GRIP, y = SIMS)) +
  geom_point() +
  labs(title = "SIMS ~ ARM + GRIP",x = "ARM + GRIP",y = "SIMS") + 
  theme(plot.title = element_text(hjust = 0.5, size = 20)) +
  geom_smooth(method=lm) 
```

We can see here that all of the data is positively correlated at a glance but we do not know which of these is the best fit for our desired prediction.

## Numerical Results

```{r}
cor(SIMS~ARM,data=mydata)
cor(SIMS~GRIP,data=mydata)
cor(SIMS~ARM+GRIP,data=mydata)
```

Given these correlation coefficients we can show that the model 3 has the psrongest correlation, 1 being a one to one relationship 0.7 is the closest we have here.

## Inferential Results

```{r}
cat("Model 1")
summary.lm(model1)
predict(model1,target1,interval=c("prediction"))
cat("4.8 = Difference")

cat("Model 2")
summary.lm(model2)
predict(model2,target1,interval=c("prediction"))
cat("5.2 = Difference")

cat("Model 3")
summary.lm(model3)
predict(model3,target1,interval=c("prediction"))
cat("4.6 = Difference")
```

Here with our linear models of the data constructed from models 1 through 3 we have several metrics to see which model best fits our data. 

We can compare Residual Standard Error which model 3 has the lowest at $\approx 1.1$, Adjusted R-Squared which is closest to one at $\approx0.5$

Finally we constricted a target at an arbitrary point an interval prediction. We see that model three has the smallest difference in the lower and upper bounds of the prediction at $\approx4.6$.

```{r}
cat("Model 1 & 2 ")
anova(model1,model2)
cat("\n\n\n Model 2 & 3 ")
anova(model2,model3)
cat("\n\n\n Model 1 & 3 ")
anova(model1,model3)
```


# Conclusion and Discussion