---
title: "Linear Model with Prediction"
author: "Ezra Licciardi"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```

```{r, eval=TRUE, warning=FALSE}
url <- "https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt"
mydata <- read.csv(file=url,sep="",header=TRUE)  
```

# Introduction

We are looking at data procured from RVLS regarding "Physical Strength and Job Performance". We are exploring this data to see if any statistically significant correlations exist in the data or if the data is meaningfully related.

$H_0$ There are no statistically meaningful relation in the data.

$H_A$ There are statistically meaningful relation in the data.


# Methods

```{r}
glimpse(mydata)
```



# Results

## Graphical Results

## Numerical Results

## Inferential Results

# Conclusion and Discussion